A Comparsion of Traffic Engineering Methods for Application Perceived Metrics

### 2015-06-10 tepaper/multisource_capacity.tex
Initial import of thesis starting from proposal document
Includes all files: tex, pdf, etc.

\section{OtherLPs}

\subsection{Other linear programs}

\subsubsection{Linear program to calculate optimal routing for flows with multiple sources}

\label{sec:lpminmlu}

Network  $G = (V,E)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Linear program to calculate MLU optimizing flow splits among multiple sources for a given routing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The variables defined above are reused for this program. We define a new set of variables for the routing to be configured.

@@

\textbf{Minimize:}  $\alpha$, the maximum link utilization.
Subject to:
\begin{enumerate}
\item 
Each flow must be routed: For each flow $f_i$,
\[ f_i = \sum_{j = 1 \mbox{ to }k }  f_{is_{ij}}, 0 \leq  f_{is_{ij}} \leq f_i \]
where each $f_{is_{ij}}$ amount of flow $f_i$ routed from source node $s_{ij}$ to destination node $t_i$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Linear Program to calculate best 'k' locations which minimize MLU}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\textbf{Problem Description}

The problem is to find the best 'k' locations among 'n'  nodes in the network to host content in the network. 
The input to the problem is a set of traffic demands represented as flows ${f_1,f_2,....}$  where flow $f_i$ is the total demand for the $i$-th flow but we do not know the set source nodes for each flow. Other inputs are similar to the previous two programs. 
\newline
\newline
\textbf{Known parameters}
Network  $G = (V,E)$.

Nodes $V = \{ n_1, n_2, ... \}$

Flow demands $F = \{f_1, f_2, ... \}$

Destination for flow $f_i$ is node  $t_i$.
\newline
\newline
\textbf{Variables:}

${x_j}$ - If $x_j = 1$ node $j$ is a source node and $x_j = 0$ otherwise.

$p_{ij}$ - Fraction of flow $f_i$ which is routed from node $j$. Note that if $x_j = 0$, $p_j$ must be zero.

$\alpha$, the maximum link utilization.
\newline
\newline
\textbf{Linear program:}
For the above network and traffic demands, we have to solve the following linear program.
\newline
\newline
Minimize:  $\alpha$
\newline
\newline
Subject to:
\begin{enumerate}
\item 
Each flow demand must be routed. For each flow $f_i$,
\[ 1 = \sum_{i = 1 to k }  p_{ij}, \mbox{ where } 0 \leq p_{ij} \leq 1 \]

\item 
Treat each flow as an independent flow which can be routed independently. For flow $p_{ij}$, . The constraints for routing this flow are :

For each node $q$,
\[ \sum_{r \in outgoing(q)} h_{qr}^{ij} - \sum_{p \in incoming(q)} h_{pq}^{ij} = d\]
(a)  if $q = j$ then $d = -p_{ij} f_i$, (b) if $q = t_i$ then, $d = p_{ij} f_i$ , (c) otherwise $d = 0$.

In addition $0 \leq h_{pq}^{ij} \leq p_{ij} f_i $ as mentioned above.

\item
(Total flow on each link) $\leq $ $\alpha $ (capacity of link). For each link $e_{pq}$, 
\[ \sum_{i,j} h_{pq}^{ij} \leq \alpha \times c_{pq} \]
for each link.

\item
There must be $k$ sources.

\[\sum_{j}  x_j = k , \mbox{ where } 0 \leq x_j \leq 1 \]

\item
If $x_j = 0$, then $p_{ij} = 0$. If $x_j$ = 1, then $p_{ij}$ can be between zero and one.
\[ p_{ij} \leq x_j \]

>>>>

\section{APPENDIX}
\label{sec:appendix}
\subsection{Linear program to calculate optimal routing for flows with multiple sources}
Network  $G = (V,E)$.

@@

\subsection{Linear program to calculate optimal MLU for a given routing}
The variables defined above are reused for this program. We define a new set of variables for the routing to be configured.

@@

Minimize:  $\alpha$, the maximum link utilization.
Subject to:
\begin{enumerate}
\item \item 
Each flow must be routed: For each flow $f_i$,
\[ f_i = \sum_{j = 1 \mbox{ to }k }  f_{is_{ij}}, 0 \leq  f_{is_{ij}} \leq f_i \]
where each $f_{is_{ij}}$ amount of flow $f_i$ routed from source node $s_{ij}$ to destination node $t_i$.

@@

\end{document}
